Letter to the Editor

### 2023-01-24 editorial-communication/response-to-the-reviewers.Qmd

---
title: "Response to the reviewers"
date: today
date-format: long
number-sections: false
format: 
  html:
    theme: 
      - cosmo 
      - custom.scss
    highlight-style: tango
    embed-resources: true
---

@@

##### As a long-term but sporadic GitHub user myself, I agree with most of the points and cases presented in the paper.

##### **E1.1.** I agree with Reviewer 1 that these could be streamlined somewhat into a smaller number of more generalizable cases. They also are a bit heavily weighted towards more experienced users. "Simple" operations like push, pull, and commit are rarely understandable to new users, who routinely forget to commit their actions. The GitHub Desktop app makes many of the operations and use of GitHub somewhat easier, and is a good entree into GitHub and Git for novices. More could be made of the desktop app. {#sec-E1.1}

::: {#ResponseE11 .response}
<!--# TODO: edit once sections get merged -->

**Response**: Thank you for these comments.
We agree that the use cases and the jargon could be simplified to make the text more readable and attractive.
Too address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows, directing readers to other references containing more technical and in-depth information about these platforms; (2) decreased the number of use cases (see [response to R1.1](#sec-R1.1) and [response to R1.2.](#sec-R1.2)); (3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction (between lines XXX and XXX).
:::

@@

##### **R1.1.** I would, however, recommend some restructuring and shortening. As it stands, this paper is too long and some of the use cases are too nerdy to spark enthusiasm in somebody who is not already using GitHub. Breaking it into 13 use cases leads to some repetition and those use cases may be combined more effectively for convincing a new user. {#sec-R1.1}

::: {#ResponseR11 .response}
In order to reduce repetition and jargon in the use cases sections, we've added a paragraph to the introduction <!--# add line numbers --> explaining a basic git & GitHub workflow and pointing the reader to other resources for learning these tools.
This allows us to focus less on explaining the specific mechanisms of git/Github in the use cases sections and more on the usefulness of the tools.
In regards to the specific suggestion about deprioritizing GitHub communication tools, we believe these are extremely useful alternatives to reply-all email chains for a variety of reasons and have attempted to improve the clarity of this section of our manuscript \[end of project management section\].
:::

##### **R1.2.** The title and abstract gave me the impression that the goal is to convince EEB researcher to start using GitHub. If that's the case, it might be better to tailor the use cases to that entry level and use less GitHub specific lingo. Advanced usage may be mentioned but not detailed as much as it is currently done. E.g. collaboratively writing a paper in GitHub is probably out of the question for most. Most GitHub options for communication, discussion, issue tracking are still somewhat esoteric for most non-programmers. {#sec-R1.2}

::: {#ResponseR12 .response}
As mentioned above ([R1.1](#sec-R1.1), [E1.1](#sec-E1.1)), we were able to reduce jargon by making it clear in the introduction that our aim was not to *teach* the use of git and GitHub, and by discussing a basic git workflow early on.
:::

@@

##### **R1.3.** Although the abstract states 'We outline features ranging from low to high technical difficulty' the paper reads a bit like a laundry list of what GitHub can do (in fact, the word 'can' is used about 140 times, which makes for tedious read). Figure 2 helps sort through this laundry list and defines the technical difficulty. It might be better to clearly lay out where anybody can start using GitHub effectively in the text. And the emphasis is on 'effectively'. Most people are not likely to learn a new piece of software if it does not promise to reduce effort and time. So, defining tasks where GitHub shines in terms of return on investment maybe the better approach to convincing new users and then only mention the advance use cases with some pointers to further reading, but not going into too much detail. {#sec-R1.3}

::: {#ResponseR13 .response}
We appreciate this comment and while we do agree that ordering the use cases by value to the reader would be ideal, we believe that value or return on investment is subjective and varies among fields, labs, and individuals.
For example, the reviewer sees collaborative writing of a manuscript using GitHub as an "out of the question" advanced use.
However, all of the co-authors on this manuscript have done exactly this and found it an excellent return on investment.
At the same time, not all co-authors have experience in many of the other use cases we present and may find them less useful depending on their needs.
We do make an attempt to quantify the investment effort in Figure 2 already.
We've added a supplemental document better explaining *how* we made these quantifications (see also our response to reviewer 2 [R2.2](#sec-R2.2)).
However, we have taken the advice of reviewer 1 in other comments ([R1.4](#sec-R1.4), [R1.1](#sec-R1.1)) to reduce the number of use cases and re-order them.
:::
